Assignment 2

### 2025-03-27 code/reddit_project/Reddit_eda.qmd
assignment 3 materials

total_posts |> 
  ggplot( aes(x = date_utc, y = total, color= Posts)) + 
  geom_point(size = 3) +  
  geom_line(linewidth = 1) +  
  labs(
    title = "Total Number of Posts per Day Pre and Post Processing",
    x = "Day",
    y = "Total Number of Posts") +
  scale_color_viridis_d(option="C", end=.8) + 
  theme_hc()

@@

comments_data_clean |> 
  group_by(date_utc) |> 
  reframe(total = n()) |> 
  ggplot( aes(x = date_utc, y = total)) + 
  geom_point(size = 3) +  
  geom_line(linewidth = 1) +  
  labs(
    title = "Total Number of comments per Day during collection",
    x = "Day",
    y = "Total Number of Posts") +
  scale_color_viridis_d(option="A") +
  theme_hc()

>>>>

total_posts |> 
  ggplot( aes(x = date_utc, y = total, color= Posts)) + 
  geom_point(size = 3) +  
  geom_line(linewidth = 1) +  
  labs(
    title = "Total Number of Posts per Day Pre/Post Processing",
    x = "Day",
    y = "Total Number of Posts") +
  scale_color_viridis_d(option="C", end=.8) + 
  theme_hc()

@@

comments_data_clean |> 
  group_by(date_utc) |> 
  reframe(total = n()) |> 
  ggplot( aes(x = date_utc, y = total)) + 
  geom_point(size = 3) +  
  geom_line(linewidth = 1) +  
  labs(
    title = "Total Number of collected comments per Day",
    x = "Day",
    y = "Total Number of Posts") +
  scale_color_viridis_d(option="A") +
  theme_hc()
